Simulation-WTCCC-2

### 2020-04-05 analysis/simulation-WTCCC.Rmd
fix description typo

## Simulate cis-expression 
We simulate cis-expression based on the following model:

$$ X' = G\alpha$$
For each gene, we sample $L$ eQTLs for this gene, for eQTL $k$, we have
$$ \alpha_k \sim N(0,\sigma_\alpha^2) $$
$$ \xi \sim N(0,1) $$
Then we have the heritability of the gene:

@@

For $\alpha$, we used the same as used in simulating expression (Thus, not $\tilde{X}$). $\gamma \sim N(0,\sigma_\gamma^2), \theta \sim N(0, \sigma_\theta^2), \epsilon \sim N (0,1)$. To choose proper $\sigma_\gamma$ and $\sigma_\theta$. We used the following formula:

>>>>

## Simulate expression 
We simulate expression based on the following model:

$$ X = G\alpha + \xi$$
For each gene, we sample $L$ eQTLs for this gene, for eQTL $k$, we have
$$ \alpha_k \sim N(0,\sigma_\alpha^2) $$
$$ \xi \sim N(0,1) $$
Then we have the heritability of the gene:

@@

For $\alpha$, we used the same as used in simulating expression. $\gamma \sim N(0,\sigma_\gamma^2), \theta \sim N(0, \sigma_\theta^2), \epsilon \sim N (0,1)$. To choose proper $\sigma_\gamma$ and $\sigma_\theta$. We used the following formula:

### 2020-04-05 analysis/simulation-WTCCC2.Rmd
fix description typo

## Simulate cis-expression 
We simulate cis-expression based on the following model, using 500 samples from cad in WTCCC:

$$ \tilde{X} = G\alpha + \xi$$
For each gene, we sample $L$ eQTLs for this gene, for eQTL $k$, we have
$$ \alpha_k \sim N(0,\sigma_\alpha^2) $$
$$ \xi \sim N(0,1) $$
Then we have the heritability of the gene:

@@

## Simulate quantitative phenotype
We simulate phenotype using bd data from WTCCC following
$$Y = G\alpha\gamma + G\theta + \epsilon$$. For $\alpha$, we used the same as used in simulating expression (Thus, not $\tilde{X}$). $\gamma \sim N(0,\sigma_\gamma^2), \theta \sim N(0, \sigma_\theta^2), \epsilon \sim N (0,1)$.

>>>>

## Simulate expression 
We simulate expression based on the following model, using 500 samples from cad in WTCCC:

$$ X = G\alpha + \xi$$
For each gene, we sample $L$ eQTLs for this gene, for eQTL $k$, we have
$$ \alpha_k \sim N(0,\sigma_\alpha^2) $$
$$ \xi \sim N(0,1) $$
Then we have the heritability of the gene:

@@

## Simulate quantitative phenotype
We simulate phenotype using bd data from WTCCC following
$$Y = G\alpha\gamma + G\theta + \epsilon$$. For $\alpha$, we used the same as used in simulating expression. $\gamma \sim N(0,\sigma_\gamma^2), \theta \sim N(0, \sigma_\theta^2), \epsilon \sim N (0,1)$.
